\documentclass{article}
\usepackage{hyperref}
\usepackage{enumitem}

\title{Deepfake Datasets: User Guide}
\author{ANAND M K - 242CS008}

\date{}

\begin{document}

\maketitle


\section{Datasets Overview}

The following deepfake datasets are available for download and usage:

\begin{itemize}
    \item \textbf{UADFV Dataset} \\
    \textbf{Description:} The UADFV (Unaltered and DeepFake Video) dataset contains deepfake videos and images created using various face-swapping techniques. This dataset is useful for performing statistical analysis of the quality and characteristics of deepfake images and videos. \\
    \textbf{Download Link:} \url{https://www.kaggle.com/datasets/adityakeshri9234/uadfv-dataset/data}
    
    \item \textbf{FaceForensics++} \\
    \textbf{Description:} FaceForensics++ is a large-scale dataset with manipulated videos containing real and deepfake faces. It includes several manipulation techniques, allowing for statistical comparisons and analysis of deepfake video attributes. \\
    \textbf{Download Link:} \url{https://www.kaggle.com/datasets/hungle3401/faceforensics}

    \item \textbf{OpenForensics} \\
    \textbf{Description:} OpenForensics is a dataset containing manipulated face images, primarily aimed at studying the statistical properties of deepfake images. It provides a diverse set of manipulations to analyze various deepfake techniques. \\
    \textbf{Download Link:} \url{https://github.com/ltnghia/openforensics} \\
    \textbf{Google Drive Link:} The dataset is hosted on Google Drive for easier access. You can download the data directly using the following link: \url{https://drive.google.com/drive/folders/1RjHbark1MKihDtAN3HJovzBCi5PGPW6E}
\end{itemize}

\section{How to Use the Datasets}

Follow the instructions below to download and use each dataset for statistical analysis:

\begin{enumerate}[label=\arabic*.]
    \item \textbf{UADFV Dataset:}
    \begin{itemize}
        \item Visit the dataset page on Kaggle using the provided link.
        \item Click on the "Download" button to get the data files.
        \item The dataset includes both real and deepfake videos/images, which can be used for statistical analysis of deepfake characteristics.
    \end{itemize}

    \item \textbf{FaceForensics++:}
    \begin{itemize}
        \item Go to the FaceForensics++ dataset page on Kaggle.
        \item After signing in to your Kaggle account, click on "Download."
        \item Make sure you have enough storage space as this dataset is quite large.
        \item The dataset contains deepfake videos that can be used for various statistical comparisons, such as temporal and quality analysis.
    \end{itemize}

\item \textbf{OpenForensics:}
\begin{itemize}
    \item The OpenForensics dataset is hosted on GitHub, and the repository contains a link to download the dataset via Google Drive.
    \item You can access and download the data directly from the Google Drive link provided in the GitHub repository. Ensure you have sufficient storage for the data.
\end{itemize}

\end{enumerate}


\end{document}
